
By March 1st, 2019 (only after reveiving access data for TUMonline and TUM regisration number---``Matrikelnummer'')
\begin{enumerate}
\item Transfer the \emph{Student Services Fee} \& \emph{solidary fee for semester ticket}: \euro{129,40} in total
\item German national health insurance (send the proof of insurance called ``Versicherungsbescheinigung'' via email to \href{mailto:alagha@zv.tum.de}{alagha@zv.tum.de} by mentioning your name and your TUM regisration number ``Matrikelnummer''.)
\item Up--load a photo in TUMonline
\end{enumerate}
% NOTE:
% After you logged into TUMonline, a new application form appears. Please DO NOT fill out this online application form in TUMonline!! Please ignore/cancel this step!!!

Following are quoted from a letter from Ms. Alagha:
\begin{quotation}
Access data (link \& username \& password) {\color{gray}(to TUMonline, added by Li Mingyang)}:
\begin{itemize}
\renewcommand\labelitemi{--}  % Following https://tex.stackexchange.com/questions/62496/itemize-with-a-dash-instead-of-a-bullet
\item Will be sent out via e-mail from it-support soon (it-support@tum.de)!
Please check also your spam folder!\\
Please \textbf{wait for it}: also if your friends already might have received the access data, please be patient!
\item \textbf{Password need to be {\color{blue}utilized and changed within a few days upon receipt}, otherwise it will get useless!}
\item if you already registered for TUMonline by mistake, you will not receive new access data. Please login in TUMonline with the same access data you used for the registration.
\end{itemize}
 
\textbf{Important:}\\
After you logged in TUMonline a new application form appears: Please \textbf{DO NOT} fill in this online application form!! Just \textbf{\color{blue}ignore/cancel this step}!!! So please do \textbf{NOT} enter any personal data in TUMonline! Just upload a photo as mentioned below.
\end{quotation}

Following are quoted from the email ``Wichtige Informationen für Ihr Austauschstudium an der TUM /important information for your exchange at TUM'':
\begin{quotation}
  Proof of enrollment (“Immatrikulationsbescheinigung”: proof that you are a TUM student)
  \begin{itemize}
  \item Wait for the e-mail that you are enrolled (from mid- March on)
  \item Log in on TUMonline with your access data -- please do not fill out a new online application on TUMonline, just cancel this step!
  \item Download the “proof of enrollment” from your TUMonline account under “prints for students” (e.g. to apply for your residence permit, open a bank account, etc.)
  \end{itemize}
\end{quotation}